---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# stat545BLunaPackage

<!-- badges: start -->
<!-- badges: end -->

The goal of stat545BLunaPackage is to group and sort a data frame

## Installation

The stat545BLunaPackage is not available on CARN yet.

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("stat545ubc-2021/stat545BLunaPackage", ref="0.1.0")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(stat545BLunaPackage)
## basic example code
library(datateachr)
### this example group the vancouver_trees by its genus_name, and then sort by the count
group_and_sort_by_count(vancouver_trees, genus_name)
```

The package will do the check on the arguments.
For function *group_and_sort_by_count*, the first argument should be a data frame, and the second one should not be empty.
Below are the examples which will throw error.
```{r, error=TRUE}
group_and_sort_by_count(vancouver_trees) ## it will throw a missing error since the second argument is missing

group_and_sort_by_count("aaaa", 1) ## it will throw an error since the first argument is not a data frame

```
